Syntax and Semantics of Cedille

### 2020-12-26 docs/semantics/paper.tex
docs: semantics: in CBN normalization, make context empty
The original can be recovered by weakening

\begin{theorem}[Call-by-name normalization of functions]
  \label{thm:cedille-termination}
  Suppose \(\Gamma\vdash t : T\), $t$ is closed, and there exists a closed term
  $t'$ which erases to \(\lambda x.\ x\) and whose type is $T \to \Pi x : T_1.\
  T_2$ for some $T_1, T_2$. Then $|t|$ is call-by-name normalizing.
  \end{theorem}

>>>>

\begin{theorem}[Call-by-name normalization of functions]
  \label{thm:cedille-termination}
  Suppose \(\cdot \vdash t \tpsynth T\) and there exists a closed term \(t'\)
  such that \(\cdot \vdash t \tpsynth T \to \abs{\Pi}{x}{T_1}{T_2}\) for some
  \(T_1,T_2\) and \(|t'| = \absu{\lambda}{x}{x}\).
  Then \(|t|\) is call-by-name normalizing.
\end{theorem}
